---
title: "WHERE IS THE CURVE FLATTENING?"
output: 
  html_document: 
    css: style.css
lang: es-CO
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(gt)
library(reactable)
library(repmis)
library(dplyr)
library(knitr)

source("code/graficos_latam.R")

Sys.setlocale(locale = "es_ES.UTF-8")
```

<h2 style = color: #000000;>
    New <span style = "color: #e61b72"><b>confirmed</b></span> cases per week 
</h2>


```{r, include=T, echo = F,  fig.height = 21, fig.width = 20}
curva_confirmados
```
<small><small><small>
Own elaboration with data from [Jhons Hopkins University](https://github.com/CSSEGISandData/COVID-19)
</small></small></small>
<br>
<br>

<h2 style = color: #000000;>
    New<span style = "color: #e61b72"><b> deaths</b></span> per week
</h2>

```{r, include=T, echo = F,  fig.height = 21, fig.width = 20}
curva_fallecidos
```
<small><small><small>
Own elaboration with data from [Jhons Hopkins University](https://github.com/CSSEGISandData/COVID-19)
</small></small></small>
<br>
<br>
<br>

<h2 style = color: #000000;>
    Data with useful indicators for<span style = "color: #e61b72"><b> 188 countries around the world </b></span> Daily update
</h2>
 
<small><small>Each country has a black triangle that, when clicked on, displays two options: Confirmed cases and Deaths; the numbers in parentheses show the days that are recorded for each country and category. If you click on the triangle of 'Confirmed cases' and / or 'Deaths,' you will be able to see the complete database.</small></small>

```{r, echo=F, warning=F, message=F}
library(reactable)
codigos <- read_csv("input/codigos_covid_paises.csv")
codigos %<>% dplyr::select(pais_region = country_region, pais_nombre_corto)


df_mundo %>%
  merge(., codigos, all.x = T) %>% 
  mutate(
    "Infections / Deaths per million inhabitants" = casos_acumulados/poblacion * 1000000,
    "Infections / Deaths per million inhabitants" = round(`Infections / Deaths per million inhabitants`, 0), 
    base = str_to_title(base)
  ) %>% 
  dplyr::select(
    `Country` = pais_region, Measurement = base, Date = fecha, `Total weeks since Patient 0` = total_semanas,  `Infections / Deaths per million inhabitants`, `Accumulated Cases` = casos_acumulados, 
    `New cases` = incidencia
  ) %>% 
  mutate(
    Measurement = str_replace(Measurement, "Confirmados", "Confirmed"),
    Measurement = str_replace(Measurement, "Fallecidos", "Deaths"),
  )
  arrange(`Country`, desc(Date)) %>% 
  reactable(groupBy = c("Country", "Measurement"),
            language = reactableLang(
              searchPlaceholder = "Search country",
              noData = "Not found"
            ),
            searchable = TRUE,
            striped = TRUE,
            highlight = TRUE,
            bordered = TRUE,
            theme = reactableTheme(
              borderColor = "#dfe2e5",
              stripedColor = "#f6f8fa",
              highlightColor = "#f0f5f9",
              cellPadding = "8px 12px",
              style = list(
                fontFamily = "Open Sans",
                fontSize = "14px"
              ),
              searchInputStyle = list(width = "100%")
            )
  )
```

